The Linux Programming Interfaces

### 2018-10-17 CS/TLPI.tex
9.27

>>>>

\section{File I/O}
Keypoints:
\begin{itemize}
\item System call APIs to perform file I/O.
\item File descriptor.
\end{itemize}

\subsection{Overview}
Key word:\textit{file descriptor}

\setcounter{section}{40}
\section{Fundamentals of Shared Libraries}

\subsection{Object Libraries}
\book{833}
\textbf{Object Library}: A set of object files.\\
\subsection{Static Libraries(archives)}
\subsubsection*{Creating and maintaining a static library}
Syntax:
\begin{lstlisting}
\$ ar \textit{options archive object-files}
\end{lstlisting}
\textbf{Conventional form of static libraries}: lib\textit{name}.a.
\begin{lstlisting}
	\$ gcc -g -c mod1.c mod2.c
	\$ ar r libdemo.a mod1.o mod2.o
	\$ rm mod1.o mod2.o
\end{lstlisting}
Delete modules from the archive:
\begin{lstlisting}
	\$ ar d libdemo.a mod2.o
\end{lstlisting}

\subsubsection*{Using a static library}
Basic way:
\begin{lstlisting}
\$ gcc -g -c prog.c
\$ gcc -g -o prog prog.o libdemo.a
\end{lstlisting}
Alternative way:
\begin{lstlisting}
\$ gcc -g -o prog prog.o -ldemo
\end{lstlisting}
'-ldemo' means '-l' and archive without lib prefix and .a suffix which resides in one of the standard directories(e.g. /usr/lib)

\subsection{Overview of Shared Libraries}
\subsection{Creating and Using Shared Libraries}
\textbf{ELF(Executable and Linking Format shared libraries)}:ELF is the format employed for executables and shared libraries on modern linux.
\subsubsection{Creating a Shared Library}
\begin{lstlisting}
\$ gcc -g -c -fPIC -Wall mod1.c mod2.c mod3.c
\$ gcc -g -o -shared -o libfoo.so mod1.o mod2.o mod3.o
\end{lstlisting}
\textbf{Remark.} Unlike static libraries, object modules cannot be add or deleted from previously built shared library(why?)\\
\subsubsection{Position-Independent Code}
\textit{-fPIC} specifies that the compiler generate position-independent code.
How to check whether an object file has been compiled with \textit{-fPIC}\book{882}

\subsubsection{Using a Shared Library}
Two main steps to utilize shared library:
\begin{itemize}
\item Embedding the name of the shared library inside the executable during linking.
\item Resolving the embedding library name: performed by \textit{dynamic linker}, named \textbf{/lib/ld-linux.so.2}.
\end{itemize}
\textbf{The LD\_LIBRARY\_PATH} enveironment variable. \book{840}

\subsubsection{The Shared Library Soname}
